Solving Variational Inequalities and Cone Complementarity Problems in Non-Smooth Dynamics using the Alternating Direction Method of Multipliers

### 2021-02-17 2021/ADMM_journal/responses_to_reviewers.tex

%% Document ----------------------------------------------
\begin{document}

\maketitle

% Sections

We would like to thank the reviewers for their thoughtful comments and
efforts towards the improvement of our manuscript. In the following document we include
our replies to their comments, where the {\color{mycommentcolor} light text color} (in italic font) is used
for the original comment from the reviewers.

In the PDF of the revised manuscript, changed text is typed in {\color{blucolor} blue color} for easier comparison with the first version.
